\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-09 doc/sw-cfhtls.tex
Done conclusions. Some rewording #203

We report the discovery of gravitational lens candidates from the
the first \sw lens search. In this search, volunteers are shown
$g-r-i$ color images of random regions of the sky taken by the CFHT Legacy
Survey. The aim of this blind lens search is to find lenses that have been
missed by previous searches done on the \cfhtls with lens finding
algorithms. In this search, we use a training sample to train the
volunteers and calibrate their performance which helps us in more
efficient pruning of the lens candidates. The training sample has
simulated lenses, duds and FPs. In this paper, we describe the details
of the training sample generated and tuned for the \cfhtls data.
Volunteers receive feedback messages when they click or fail to click on
the training images during live classification of real images which
helps them remain focused and improve their performance over time. More
details about the design of \sw system and how it works are given in the
companion paper, \PaperOne.

The blind lens search in the \cfhtls is done in two stages: \StageOne and
\StageTwo. In \StageOne, volunteers inspected $\sim$ 430 000 images and
selected a smaller sample of $\sim$ 3000 images with interesting lens
candidates. In \StageTwo, after a careful reinspection of the candidates
from \StageOne, a smaller pool of more pure sample of $\sim$~500
candidates is obtained. In the next step, the images are graded by three
lens experts (AM, AV and PJM) producing candidates with quality flags
ranging from possibly a lens to almost certainly a lens.

In this paper, we present the new \sw sample and compare it
with the previously known samples from two robotic searches from the
\cfhtls namely, the \rf and \af. More detailed description and analyses
of the new sample such as spectroscopic confirmation and mass modelling
analyses will be presented in a subsequent \sw paper (Verma et al., in
prep.).

Below, we give some of our conclusions from the first \sw lens search
and the comparison with robotic searches:
\begin{itemize}

@@

\item We present a sample of {\bf 59 new} gravitational lens candidates
out of which {\bf 29} are more promising systems. These candidates received
averaged grades, G$\ge$1.3 from three experts where 1-possibly, a lens,
2-probably, a lens and 3-certainly, a lens. In addition, among the
G$\ge$1.3 sample, we find 83 lens candidates from the various samples
published in the literature.

\item Compared to the sample of robotically (the \rf and \af) detected
lens candidates, the \sw sample finds lens systems with similar range in
the lens redshift and properties of the lensed images such as the total
magnitude and the Einstein radii. However, the \sw search being a purely
visual one cannot find some of the \rf-identified-lensed images with
sub-arcsecond $R_{\rm E}$ because the flux of the typically faint
lensed images is obscured by the flux from bright lensing galaxies. The
\rf finds these candidates because it works with lensing
galaxy-subtracted images.

\item Qualitatively, the \sw sample finds lens systems with different
types of lensing galaxies, for example, elliptical, spiral (face on and
edge on) and small red galaxies unlike those found from robotic
searches. Similarly, the lensed images too have diverse properties such
as different colors, morphologies and sizes which are again typically
missed by any given algorithm.

\item Based on the known sample of lenses and lens candidates, we find
that we lose a very small fraction of them as we go from \StageOne to
\StageTwo. In other words, it is more important to improve the lens
detection efficiency right at \StageOne to increase the overall
completeness of the final lens sample

\item From the sample of known lenses, \sw missed about 40~per~cent at \StageOne.
Among the missed sample of about 20 lenses, roughly half of them are
visually difficult to identify because most of them are faint with small
image separations which are identified through the \rf

\item If we use the classifications from the high power volunteers alone
at \StageOne, then we recover over 30~per~cent of the lenses from the missed
sample. Thus, it is possible to improve the completeness of lenses by
changing the strategy of when and who is shown an image.

@@

The discovery of several new candidates through the first \sw lens
search has demonstrated that the citizen scientists have successfully
taught themselves to identify lenses within a short span of time and
that they have found lens candidates which the algorithms failed to
discover.  However, the upcoming and planned imaging surveys such as the
DES, HSC and LSST will have formidable amount of data. Any one approach
for finding lenses is likely going to be inefficient. Thus, combining
robotic methods for pre-selection with the citizen science approach for
visual screening will be an optimal choice for finding lenses in these
large imaging surveys.

@@

{\bf The redshifts with $^s$ are spectroscopic estimates taken from SDDS Data

@@

SW19 & CFHTLS J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\
SW8 & CFHTLS J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\
SW43 & CFHTLS J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\
SW9 & CFHTLS J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\
SW10 & CFHTLS J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\
SW11 & CFHTLS J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\
SW44 & CFHTLS J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\
SW30 & CFHTLS J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\
SW20 & CFHTLS J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\
SW45 & CFHTLS J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\
SW46 & CFHTLS J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\
SW31 & CFHTLS J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\
SW32 & CFHTLS J022359.8$-$083651 &  35.99955 &  $-$8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\
SW12 & CFHTLS J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\
SW1 & CFHTLS J022409.5$-$105807 &  36.03978 & $-$10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\
SW21 & CFHTLS J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\
SW22 & CFHTLS J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\
SW33 & CFHTLS J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\
SW13 & CFHTLS J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\
SW47 & CFHTLS J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\
SW23 & CFHTLS J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\
SW14 & CFHTLS J023123.2$-$082535 &  37.84682 &  $-$8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\
SW24 & CFHTLS J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\
SW34 & CFHTLS J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\
SW35 & CFHTLS J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\
SW15 & CFHTLS J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\
SW48 & CFHTLS J090219.0$-$053923 & 135.57947 &  $-$5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\
SW36 & CFHTLS J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\
SW25 & CFHTLS J090308.2$-$043252 & 135.78449 &  $-$4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\
SW49 & CFHTLS J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\
SW50 & CFHTLS J090333.2$-$005829 & 135.88869 &  $-$0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\
SW51 & CFHTLS J135724.8+561614 & 209.35374 &  56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\
SW26 & CFHTLS J135755.8+571722 & 209.48268 &  57.28971 &  0.8 & 21.4 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\
SW52 & CFHTLS J140027.9+541028 & 210.11636 &  54.17455 &  0.6 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\
SW16 & CFHTLS J140030.2+574437 & 210.12601 &  57.74371 &  0.38$^s$ & 18.8 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\
SW2 & CFHTLS J140522.2+574333 & 211.34261 &  57.72587 &  0.52$^s$ & 20.3 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\
SW17 & CFHTLS J140622.9+520942 & 211.59581 &  52.16169 &  0.7 & 21.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\
SW27 & CFHTLS J141432.9+534004 & 213.63716 &  53.66788 &  0.7 & 22.1 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\
SW53 & CFHTLS J141518.9+513915 & 213.82903 &  51.65420 &  0.29$^s$ & 18.9 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\
SW3 & CFHTLS J142603.2+511421 & 216.51375 &  51.23935 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7 &  A,G   \\
SW54 & CFHTLS J142620.8+561356 & 216.58699 &  56.23230 &  0.5 & 19.9 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\
SW55 & CFHTLS J142652.8+560001 & 216.72004 &  56.00044 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0 &  R,R   \\
SW56 & CFHTLS J142843.5+543713 & 217.18153 &  54.62036 &  0.4 & 20.3 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\
SW4 & CFHTLS J142934.2+562541 & 217.39261 &  56.42807 &  0.51$^s$ & 19.9 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\
SW28 & CFHTLS J143055.9+572431 & 217.73332 &  57.40883 &  0.60$^s$ & 20.1 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\
SW37 & CFHTLS J143100.2+564603 & 217.75124 &  56.76750 &  0.0 &  0.0 &  1.2 &  1.7 & ASW00086xq &  0.8 &  A,E   \\
SW38 & CFHTLS J143353.6+542310 & 218.47357 &  54.38624 &  0.65$^s$ & 20.7 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\
SW5 & CFHTLS J143454.4+522850 & 218.72702 &  52.48080 &  0.62$^s$ & 20.5 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\
SW6 & CFHTLS J143627.9+563832 & 219.11636 &  56.64249 &  0.53$^s$ & 20.2 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\
SW57 & CFHTLS J143631.5+571131 & 219.13155 &  57.19215 &  0.7 & 22.0 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\
SW58 & CFHTLS J143651.6+530705 & 219.21503 &  53.11832 &  0.58$^s$ & 20.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\
SW18 & CFHTLS J143658.1+533807 & 219.24246 &  53.63550 &  0.61$^s$ & 20.3 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\
SW29 & CFHTLS J143838.1+572647 & 219.65887 &  57.44645 &  0.8 & 21.3 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\
SW59 & CFHTLS J143950.6+544606 & 219.96101 &  54.76858 &  0.73$^s$ &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\
SW39 & CFHTLS J220215.2+012124 & 330.56348 &   1.35667 &  0.31$^s$ & 18.0 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\
SW7 & CFHTLS J220256.8+023432 & 330.73691 &   2.57581 &  0.48$^s$ &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\
SW40 & CFHTLS J221306.1+014708 & 333.27579 &   1.78561 &  0.0 & 17.8 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\
SW41 & CFHTLS J221519.7+005758 & 333.83212 &   0.96615 &  0.4 & 20.8 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\
SW42 & CFHTLS J221716.5+015826 & 334.31894 &   1.97394 &  0.1 & 22.0 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\

>>>>

We report the discovery of gravitational lens candidates from the
the first \sw lens search. In this search, volunteers were shown
$g-r-i$ color images of random regions of the sky taken by the CFHT Legacy
Survey. The aim of this blind lens search was to find lenses that had been
missed by previous searches done on the \cfhtls with lens finding
algorithms.
The search was carried out in two stages.
In \StageOne, volunteers inspected $\sim$ 430,000 images, and
selected a smaller sample of $\sim$ 3000 images as having interesting lens
candidates. In \StageTwo, after a careful second inspection of the candidates
from \StageOne, a purer sample of $\sim$~500
candidates was obtained. In a final step, these images were inspected by three
of us (AM, AV and PJM) to produce a sample of candidates with grades
ranging from possibly a lens (1) to almost certainly a lens (3).
In this paper, we presented this new \sw sample and compared it
with the previously known samples from two robotic searches from the
\cfhtls, namely, \rf and \af.

Our conclusions are as follows:
\begin{itemize}

@@

\item We present a sample of {\bf 29 new} gravitational lens candidates,
and an additional 30 medium grade systems. These 59 candidates received
averaged grade G$\ge$1.3 from three experts follwing the scale
where 1 means possibly, 2 means
probably, and 3 means certainly, a lens. In addition, among the
G$\ge$1.3 sample, we re-discovered 83 lens candidates from various samples
published in the literature.

\item Compared to the sample of \rf and \af robotically detected
lens candidates, the \sw sample finds lens systems with similar properties,
including the range of
lens redshifts, lensed image total
magnitudes, and Einstein radii. However, having only displayed images without
the lens galaxy light subtracted, the \sw sample does not contain
many of the \rf-identified-lensed images with
sub-arcsecond $R_{\rm E}$, just because the flux of the typically faint
lensed images is obscured by the flux from bright lensing galaxies.

\item Qualitatively, \sw seems to have found lens systems with different
types of lensing galaxies, for example, elliptical, spiral (face on and
edge on) and small red galaxies unlike those found from robotic
searches. Similarly, the lensed images too have diverse properties such
as different colors, morphologies and sizes which are again typically
missed by any given algorithm.

\item Based on the known sample of lenses and lens candidates, we find
that we lose a very small fraction of them during \StageTwo refinement.
It is more important to improve the lens
detection sensitivity at the initial \StageOne classification step.
About 40\% of the previously known lenses (20 in total) were missed at \StageOne.
Roughly half of these missing lenses were found to be galaxy-scale \rf
systems, with faint arcs blended with the bright lens galaxies.

\item It is possible to improve the \sw completeness by
changing the strategy of when and who is shown an image: only using high power
classifications recovers 30\% of the missing lenses.

@@

The discovery of many new lens candidates through the first \sw lens
search has demonstrated that the citizen scientists have successfully
taught themselves to identify lenses within a short span of time.
They have found lens candidates which the algorithms failed to
discover.  Upcoming and planned wide-field imaging surveys such as the
DES, HSC and LSST will provide formidable amounts of data. Any one approach
for finding lenses is likely going to be inefficient. Thus, combining
robotic methods for pre-selection with the citizen science approach for
visual screening could be a good strategy for finding lenses in these
large imaging surveys.

@@

{\bf The redshifts with $^s$ are spectroscopic estimates taken from SDSS Data

@@

SW19 & CFHTLS\,J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\
SW8  & CFHTLS\,J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\
SW43 & CFHTLS\,J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\
SW9  & CFHTLS\,J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\
SW10 & CFHTLS\,J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\
SW11 & CFHTLS\,J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\
SW44 & CFHTLS\,J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\
SW30 & CFHTLS\,J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\
SW20 & CFHTLS\,J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\
SW45 & CFHTLS\,J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\
SW46 & CFHTLS\,J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\
SW31 & CFHTLS\,J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\
SW32 & CFHTLS\,J022359.8$-$083651 &  35.99955 &  $-$8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\
SW12 & CFHTLS\,J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\
SW1  & CFHTLS\,J022409.5$-$105807 &  36.03978 & $-$10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\
SW21 & CFHTLS\,J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\
SW22 & CFHTLS\,J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\
SW33 & CFHTLS\,J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\
SW13 & CFHTLS\,J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\
SW47 & CFHTLS\,J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\
SW23 & CFHTLS\,J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\
SW14 & CFHTLS\,J023123.2$-$082535 &  37.84682 &  $-$8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\
SW24 & CFHTLS\,J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\
SW34 & CFHTLS\,J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\
SW35 & CFHTLS\,J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\
SW15 & CFHTLS\,J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\
SW48 & CFHTLS\,J090219.0$-$053923 & 135.57947 &  $-$5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\
SW36 & CFHTLS\,J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\
SW25 & CFHTLS\,J090308.2$-$043252 & 135.78449 &  $-$4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\
SW49 & CFHTLS\,J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\
SW50 & CFHTLS\,J090333.2$-$005829 & 135.88869 &  $-$0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\
SW51 & CFHTLS\,J135724.8$+$561614 & 209.35374 &    56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\
SW26 & CFHTLS\,J135755.8$+$571722 & 209.48268 &    57.28971 &  0.8 & 21.4 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\
SW52 & CFHTLS\,J140027.9$+$541028 & 210.11636 &    54.17455 &  0.6 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\
SW16 & CFHTLS\,J140030.2$+$574437 & 210.12601 &    57.74371 &  0.38$^s$ & 18.8 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\
SW2  & CFHTLS\,J140522.2$+$574333 & 211.34261 &    57.72587 &  0.52$^s$ & 20.3 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\
SW17 & CFHTLS\,J140622.9$+$520942 & 211.59581 &    52.16169 &  0.7 & 21.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\
SW27 & CFHTLS\,J141432.9$+$534004 & 213.63716 &    53.66788 &  0.7 & 22.1 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\
SW53 & CFHTLS\,J141518.9$+$513915 & 213.82903 &    51.65420 &  0.29$^s$ & 18.9 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\
SW3  & CFHTLS\,J142603.2$+$511421 & 216.51375 &    51.23935 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7 &  A,G   \\
SW54 & CFHTLS\,J142620.8$+$561356 & 216.58699 &    56.23230 &  0.5 & 19.9 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\
SW55 & CFHTLS\,J142652.8$+$560001 & 216.72004 &    56.00044 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0 &  R,R   \\
SW56 & CFHTLS\,J142843.5$+$543713 & 217.18153 &    54.62036 &  0.4 & 20.3 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\
SW4  & CFHTLS\,J142934.2$+$562541 & 217.39261 &    56.42807 &  0.51$^s$ & 19.9 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\
SW28 & CFHTLS\,J143055.9$+$572431 & 217.73332 &    57.40883 &  0.60$^s$ & 20.1 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\
SW37 & CFHTLS\,J143100.2$+$564603 & 217.75124 &    56.76750 &  0.0 &  0.0 &  1.2 &  1.7 & ASW00086xq &  0.8 &  A,E   \\
SW38 & CFHTLS\,J143353.6$+$542310 & 218.47357 &    54.38624 &  0.65$^s$ & 20.7 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\
SW5  & CFHTLS\,J143454.4$+$522850 & 218.72702 &    52.48080 &  0.62$^s$ & 20.5 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\
SW6  & CFHTLS\,J143627.9$+$563832 & 219.11636 &    56.64249 &  0.53$^s$ & 20.2 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\
SW57 & CFHTLS\,J143631.5$+$571131 & 219.13155 &    57.19215 &  0.7 & 22.0 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\
SW58 & CFHTLS\,J143651.6$+$530705 & 219.21503 &    53.11832 &  0.58$^s$ & 20.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\
SW18 & CFHTLS\,J143658.1$+$533807 & 219.24246 &    53.63550 &  0.61$^s$ & 20.3 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\
SW29 & CFHTLS\,J143838.1$+$572647 & 219.65887 &    57.44645 &  0.8 & 21.3 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\
SW59 & CFHTLS\,J143950.6$+$544606 & 219.96101 &    54.76858 &  0.73$^s$ &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\
SW39 & CFHTLS\,J220215.2$+$012124 & 330.56348 &     1.35667 &  0.31$^s$ & 18.0 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\
SW7  & CFHTLS\,J220256.8$+$023432 & 330.73691 &     2.57581 &  0.48$^s$ &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\
SW40 & CFHTLS\,J221306.1$+$014708 & 333.27579 &     1.78561 &  0.0 & 17.8 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\
SW41 & CFHTLS\,J221519.7$+$005758 & 333.83212 &     0.96615 &  0.4 & 20.8 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\
SW42 & CFHTLS\,J221716.5$+$015826 & 334.31894 &     1.97394 &  0.1 & 22.0 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\
